% !TeX root = main.tex
% !TeX program = xelatex

{
    % Да сортировки не хватает,
    % но просто написать список вручную значительно удобнее
    % чем пытаться настроить кривые пакеты.
    \newcommand\bibitemsite[4]{%
        \bibitem{#1} #2 : сайт. "--- URL: #3 (дата обращения: #4). "--- Текст : электронный.
    }

    \patchcmd{\thebibliography}{\section*}{\section}{}{}
    % https://www.reddit.com/r/LaTeX/comments/gop0rg/the_symbol_with_newcommand
    \makeatletter
    \renewcommand*{\@biblabel}[1]{#1.}
    \makeatother
    \begin{thebibliography}{9}
        \bibitemsite{epics}
        {\EN{EPICS - Experimental Physics and Industrial Control System}}
        {https://epics.anl.gov/}
        {09.05.2023}
        
        %https://conferences.iaea.org/event/244/contributions/19766/contribution.pdf
        %https://www.researchgate.net/publication/224130754\_Assessment\_of\_Precise\_Time\_Protocol\_in\_a\_Prototype\_System\_for\_the\_ITER\_Neutral\_Beam\_Test\_Facility
        %https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=10017353
        \bibitem{iterptp}
        Trevisan L. et al. Assessment of IEEE 1588-based Timing System of the ITER Neutral Beam Test Facility. "--- 2023.
        
        \bibitem{rfc5905} Mills D., Burbank J., Kasch W. RFC 5905: Network time protocol version 4: Protocol and algorithms specification. "--- 2010.

        \bibitem{ieee1588} IEEE Std 1588-2019.

        \bibitemsite{ntpfaq}
        {\EN{The NTP FAQ and HOWTO}}
        {http://www.ntp.org/ntpfaq/}
        {09.05.2023}
        
        \bibitemsite{planetswitch}
        {\EN{IGSW-24040T - Rack-mount Managed Ethernet Switch - PLANET Technology}}
        {https://www.planet.com.tw/en/product/igsw-24040t-v4}
        {09.05.2023}
        
        \bibitem{ptphowbig}
        Ciarleglio N., Edwards T., Welch R. Large scale PTP: How big can it get? //SMPTE 2016 Annual Technical Conference and Exhibition. "--- SMPTE, 2016. "--- С. 1-13.

        \bibitemsite{ptpd}
        {\EN{ptpd/ptpd: PTPd official source - master branch a.k.a. trunk}}
        {https://github.com/ptpd/ptpd}
        {09.05.2023}
        
        \bibitemsite{ptp4l}
        {The Linux PTP Project}
        {https://linuxptp.sourceforge.net/}
        {09.05.2023}
        
        \bibitemsite{nxpptptimeout1}
        {\EN{ptp4l tx timestamp timeout - NXP Communit}}
        {https://community.nxp.com/t5/QorIQ/ptp4l-tx-timestamp-timeout/m-p/892488}
        {09.05.2023}
        
        \bibitemsite{nxpptptimeout2}
        {\EN{ptp  increasing tx\_timestamp\_timeout - NXP Community}}
        {https://community.nxp.com/t5/QorIQ/ptp-increasing-tx-timestamp-timeout/td-p/1368105}
        {09.05.2023}

        \bibitemsite{nxpptptimeout3}
        {\EN{[Linuxptp-users] poll tx timestamp timeout}}
        {https://linuxptp-users.narkive.com/W7lNh65D/poll-tx-timestamp-timeout}
        {09.05.2023}

    \end{thebibliography}
}
